%-------------------------
% CV - Kaviya Sathishkumar
%-------------------------

\documentclass[a4paper,11pt]{article}

%------------PACKAGES----------------
\usepackage{verbatim}
\usepackage{titlesec}
\usepackage{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}

\input glyphtounicode
\pdfgentounicode=1
\usepackage[default]{sourcesanspro}
\urlstyle{same}

%----------MARGINS-----------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0in}
\renewcommand{\footrulewidth}{0in}
\setlength{\tabcolsep}{0in}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\textheight}{1.0in}
\raggedbottom{}
\raggedright{}

%--------SECTION STYLE---------
\titleformat{\section}
  {\scshape\large}{}
  {0em}{\color{blue}}[\color{black}\titlerule\vspace{0pt}]

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\ULdepth}{2pt}

%--------CUSTOM COMMANDS--------------
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=0.11in]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeSectionType}[3]{
  \item\begin{tabular*}{0.96\textwidth}[t]{p{0.22\linewidth}p{0.02\linewidth}p{0.74\linewidth}}
    \textbf{#1} & #2 & #3
  \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeQuadHeading}[4]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}
}

\newcommand{\resumeHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeHeadingListEnd}{\end{itemize}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

%__________________RESUME____________________
\begin{document}

%-----------CONTACT------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Kaviya Sathishkumar \vspace{2pt}} &
  London, United Kingdom \\
  \href{https://linkedin.com/in/kaviya-sathishkumar/}{\uline{LinkedIn}} $|$
  \href{https://github.com/kaviya-sathishkumar}{\uline{GitHub}} $|$
  \href{mailto:kaviyashrie27@proton.me}{\uline{kaviyashrie27@proton.me}} &
  Mobile: +44 7424 544 401 \\
\end{tabular*}

%-----------SUMMARY--------------------------
\section{Professional Summary}
\small{
Highly skilled engineer with a strong foundation in IT, Python, and Azure, complemented by a MSc in International Business Management and prior SDET experience. Seeking to leverage expertise in AI/ML to lead innovative solutions within Citi Innovation Labs.
}

%--------------SKILLS------------------------
\section{Core Competencies}
\resumeHeadingListStart{}
\resumeSectionType{Technical Skills}{:}{Python, C#, SQL, Azure AI services, RAG, Langchain, Langgraph, AI models}
\resumeSectionType{MS Office Suite}{:}{PowerPoint, Excel, Word, Outlook, SharePoint, Teams}
\resumeSectionType{Soft Skills}{:}{Organisation, Excellent attention to detail, Multi-tasking, Professional Communication, Stakeholder correspondence, Cross-functional Collaboration}
\resumeHeadingListEnd{}

%-----------EDUCATION-------------------------
\section{Education}
\resumeHeadingListStart{}
  \resumeQuadHeading
    {University of East London}
    {London, United Kingdom}
    {MSc International Business Management -- Grade: 1:1}
    {May 2024 -- Jan 2026}

  \resumeQuadHeading
    {Sri Krishna College of Technology}
    {Coimbatore, India}
    {B.Tech Information Technology -- GPA: 8.05/10}
    {Aug 2019 -- May 2023}
\resumeHeadingListEnd{}

%-----------EXPERIENCE-----------------------
\section{Experience}
\resumeHeadingListStart{}
\resumeQuadHeading
  {Graduate Business Development Manager}{June 2025 -- Present}
  {EFA Engineering}{London, United Kingdom}
  \resumeItemListStart{}
    \resumeItem{Provided strategic support to senior leadership by creating impactful board presentations and client pitches, ensuring alignment between technical goals and business outcomes.}
    \resumeItem{Managed complex financial workflows, including invoicing and supplier payments, maintaining 100\% accuracy and audit readiness.}
    \resumeItem{Optimized administrative pipelines, achieving a 30\% reduction in processing time through workflow automation and enhanced organization.}
  \resumeItemListEnd{}

\resumeQuadHeading
  {Business \& Administration Officer}{Oct 2024 -- Apr 2025}
  {NextGen}{London, United Kingdom}
  \resumeItemListStart{}
    \resumeItem{Managed 200+ client accounts with a focus on data integrity, invoice processing, and meticulous financial record-keeping.}
    \resumeItem{Ensured 100\% compliance with GDPR standards while handling sensitive enterprise data and client communications.}
    \resumeItem{Developed and implemented process improvements that streamlined account management and reduced overhead by 30\%.}
  \resumeItemListEnd{}

\resumeQuadHeading
  {Software Development Engineer in Test}{Jan 2023 -- Jan 2024}
  {Nineleaps}{Bangalore, India}
  \resumeItemListStart{}
    \resumeItem{Supported enterprise software delivery within Agile/Scrum frameworks, utilizing Azure DevOps for sprint tracking and quality assurance.}
    \resumeItem{Acted as a technical bridge between developers and stakeholders to resolve blockers and ensure smooth deployment cycles.}
    \resumeItem{Authored high-quality technical documentation and test plans, establishing best practices for software reliability and team scalability.}
  \resumeItemListEnd{}

%-----------PROJECTS-------------------------
\section{Projects}
\resumeSubHeadingListStart{}
\resumeProjectHeading
    {\textbf{CRM Analytics \& Intelligence Hub} $|$ Power BI, Excel, Python, SQL}{2025}
    \resumeItemListStart
      \resumeItem{Designed KPI dashboards using Power BI and advanced Excel (Pivot Tables, Lookups, Macros) to track sales performance and client data.}
      \resumeItem{Enabled data-driven decision making by transforming raw CRM data into actionable business insights for management teams.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{AI Intelligent Calculator} $|$ Python, LLMs, Prompt Engineering}{2025}
    \resumeItemListStart
      \resumeItem{Developed an AI-powered calculator capable of interpreting natural language queries and performing contextual mathematical and logical operations.}
      \resumeItem{Applied prompt engineering techniques to improve accuracy and usability for non-technical users.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Administrative Workflow Automation Tool} $|$ Power Automate, Power Apps, Excel}{2025}
    \resumeItemListStart
      \resumeItem{Built automation workflows to streamline invoice tracking, data entry, and internal approval processes, reducing manual effort significantly.}
      \resumeItem{Integrated Microsoft tools to improve operational efficiency and ensure process standardisation across teams.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{RAG-Based CV Generation System} $|$ Python, LangGraph, LLMs, AI}{Present}
    \resumeItemListStart
      \resumeItem{Built AI-powered CV generator demonstrating knowledge of RAG pipelines and LangGraph orchestration.}
      \resumeItem{Created user guides and used stakeholder feedback to enhance usability and technical accuracy.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd{}

%-----------CERTIFICATIONS-------------------
\section{Certifications}
\resumeHeadingListStart{}
  \resumeItem{Microsoft Certified: Azure AI Engineer Associate (AI-102) -- In Progress}
  \resumeItem{Project Management -- LinkedIn Learning (2025)}
  \resumeItem{Power BI \& Excel Advanced -- LinkedIn Learning}
\resumeHeadingListEnd{}

\end{document}
